\documentclass{article}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage[utf8]{inputenc}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage{tikz}
\usepackage{pgfplots}
\pgfplotsset{compat=1.5}

\usetikzlibrary{external}
\tikzexternalize
\tikzsetexternalprefix{tikzexternal/}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage{amsmath,amsfonts,amssymb}
\renewcommand{\baselinestretch}{1.0}
\usepackage{graphicx}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{color, colortbl}
\definecolor{gray}{gray}{0.75}
\definecolor{ligray}{gray}{0.9}
\usepackage{lscape}
\usepackage{enumitem}
\usepackage{chngcntr}
\counterwithin{figure}{section}
\counterwithin{table}{section}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setlength{\parindent}{0pt}
\setlength{\parskip}{\medskipamount}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage{newtxtext,newtxmath}

% Instead of the above, use this for arXiv:

%\usepackage{txfonts}
%\usepackage{textcomp}
%\usepackage{eurosym}
%\let\texteuro\euro

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\unit}[1]{\ensuremath{\mathrm{#1}}}
\newcommand{\micron}{\mbox{$\mu$m}}
\renewcommand{\deg}{\mbox{deg}}
\newcommand{\sqdeg}{\mbox{$\deg^2$}}
\newcommand{\persqdeg}{\mbox{$\deg^{-2}$}}
\newcommand{\arcmin}{\mbox{arcmin}}
\newcommand{\sqarcmin}{\mbox{\arcmin$^2$}}
\newcommand{\persqarcmin}{\mbox{\arcmin$^{-2}$}}
\newcommand{\arcsec}{\mbox{arcsec}}
\newcommand{\sqarcsec}{\mbox{\arcsec$^2$}}
\newcommand{\persqarcsec}{\mbox{\arcsec$^{-2}$}}
\newcommand{\sqmm}{\mbox{mm$^2$}}
\newcommand{\deighty}{\ensuremath{d_{80}}}
\newcommand{\Hs}{\mbox{$H_\mathrm{s}$}}
\newcommand{\Ravg}{\mbox{$R_\mathrm{avg}$}}
\newcommand{\Tavg}{\mbox{$T_\mathrm{avg}$}}
\newcommand{\mm}{\mbox{mm}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\pagestyle{empty}

\begin{center}

{\Large \bfseries DDRAGO and WOB Product Tree}

\vspace{2cm}

\begin{tabular}{ll}
Prepared by:&Rosalía Langarica\\
&Fernando Angeles\\
&Jorge Fuentes\\
&Alan M. Watson\\
Reviewed by:&Alan M. Watson\\
&Rosalía Langarica\\
Approved by:&Alan M. Watson\\
&Rosalía Langarica\\
Reference:&\\
Version:& 2.0\\
Date:&1 February 2022\\
\end{tabular}

\vspace{\fill}

DDRAGO Project\\
Instituto de Astronomí­a\\
Universidad Nacional Autónoma de México

\end{center}

\newpage

\section*{Document Change Record}

\begin{itemize}

\item Version 2.0 of 2 February 2022.

\begin{itemize}
    \item Update for the CDR of DDRAGO and the WOB combining elements of the previous DDRAGO product tree and the DDRAGUITO product tree.
\end{itemize}

\item Version 1.0 of 16 September 2017.

\begin{itemize}
    \item Initial version.
\end{itemize}

\end{itemize}

\newpage

\section*{Applicable Documents}

\begin{enumerate}[label={AD\arabic*}]
%\item \label{FPRD} Vives, S., and R\'egal, X., ``Functional and Performance Requirements Documents", GFT-FPRD-Draft-2.0.
\item \label{optics} Fuentes-Fernández,~J., Watson, A. M., \& Cuevas, S., “COLIBRI Optical Design”, GFT-OD-A3135-040-UNAM-8.0.
\item \label{aiv} Cuevas, S., Fuentes-Fernández, J.., Watson, A. M., \& Angeles, F., “DDRAGO and WOB AIV Plan”, GFT-PL-A3135-043-UNAM-4,2.
\item \label{mechanics} Langarica, R., Farah, A., Tinoco. S., Ruíz, J., Fuentes-Fernández, J., Cuevas, S., \& Watson, A. M., “DDRAGO and WOB Mechanical Design”, GFT-MD-A3135-041-UNAM-3.1.
\end{enumerate}

%\section*{Reference Documents}

%\begin{enumerate}[label={RD\arabic*}]
%\item \label{butler12} Butler, N. Klein, C., Fox, O., et al.,``First Light with RATIR: An Automated 6-band Optical/NIR Imaging Camera'', {\it Proc. SPIE}, {\bf 8846}, 10 (2012).
%\item \label{kumler05} Kumler, Jay, ``Designing and Specifying Aspheres for Manufacturability'', {\it Proc. SPIE}, {\bf 5874}, 9 (2005).
%\item \label{yoder15} Yoder, P. R and Vukobratovich, D., ``Opto-mechanical Systems Design", CRC Press, Fourth Ed., Vol. 1, Section 11.4.3. (2015).
%\item \label{boccas06} Boccas,~M., Vucina,~T., Araya,~C.; et al.,``Protected-silver coatings for the 8-m Gemini telescope mirror'', {\it Thin Solid Films}, {\bf 502}, 275 (2006).
%\item \label{leviton15} Leviton, D. B., Miller, K. H., Quijada, M. A., et al., ``Temperature-dependent refractive index measurements of CaF2, Suprasil 3001, and S-FTM16 for the Euclid near-infrared spectrometer and photometer'', {\it Proc. SPIE}, {\bf 9578}, 12 (2015).
%\item \label{sanchez17} Sánchez, B., Keiman, C., Fuentes-Fernández, J., et al., ``Cryogenic application of an auto-centering mount working at the diffraction limit", {\it Opt. Eng.}, {\bf 56}(3), 034114 (2017).
%\end{enumerate}

\newpage

\pagestyle{plain}

\tableofcontents
\newpage

%\listoffigures
%\newpage

%\listoftables
%\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\clearpage
\section{Introduction}

This document presents the product tree for DDRAGO and the WOB.

The main primary and secondary categories are:
\begin{itemize}
\item DD-OP -- Optics.
\item DD-ME -- Mechanics.
\begin{itemize}
    \item DD-ME-SST –– Support structure
    \item DD-ME-OM$x$ -- Optomechanics for $x$
    \item DD-ME-WOB -- WOB
    \item DD-ME-MH –– Mounting hardware
    \item DD-ME-MET –– Metrology tools
\end{itemize}
\item DD-CO -- Control.
\begin{itemize}
    \item DD-CO-CR –– Control room
    \item DD-CO-CE –– Close electronics
    \item DD-CO-BDH/RDH –– Blue/red detector head
    \item DD-CO-BFW/RFW –– Blue/red filter wheel
    \item DD-CO-WOB-LS –– WOB linear stage
    \item DD-CO-WOB-SH -- WOB shutter
\end{itemize}
\item DD-TE -- Test Equipment.
\end{itemize}

For the most part, the refinement of the product codes from primary code, secondary code, and tertiary code follows the physical architecture of the instrument. However, there are exceptions:

\begin{enumerate}
\item
The optics appear under DD-OP and the optomechanics which support the optics under DD-ME.
\item
The detectors are split between DD-OP, DD-ME, and DD-CO. For example, the blue detector is split as follows:
\begin{itemize}
\item
DD-OP-BDET -- The actual CCD
\item
DD-OP-BW -- The window before the CCD
\item
DD-ME-BDETH -- The detector head supplied by Spectral Instruments. Physically, DD-OP-BDET and DD-OP-BW are components of this, but in the product tree they appear separately.
\item
DD-CO-BDET-PC -- The power cable for the detector head.
\item
DD-CO-BDET-CF -- The control fibre pair for the detector head.
\item
DD-CO-BDET-CSH -- The cryogen supply hose for the detector head.
\item
DD-CO-BDET-CRH -- The cryogen return hose for the detector head.
\end{itemize}
The red detector is similarly split.
\item
The filter wheels are split between DR-OP, DR-ME, and DR-CO. For example, the blue filter wheel is split as follows:
\begin{itemize}
\item DD-OP-FL-B -- The $B$ filter.
\item DD-OP-FL-G -- The $g$ filter.
\item DD-OP-FL-R -- The $r$ filter.
\item DD-OP-FL-I -- The $i$ filter.
\item DD-OP-FL-GRI -- The $gri$ filter.
\item
DD-ME-BFW -- The blue filter wheel mechanism supplied by FLI.
\item
\item
DD-CO-BFW-PC -- The power cable for the blue filter wheel.
\item
DD-CO-BFW-CC -- The control cable for the blue filter wheel.
\end{itemize}
The red filter wheel is similarly split.
\end{enumerate}

\end{document}